\section{DNS queries analysis}

\subsection{\texttt{salleurl.edu} DNS request}

\subsubsection{Primary name server}

TODO: Is it possible to say for sure the the primary is aries? Or is it not yet known which one is the primary one?

The primary name server for the {\tt salleurl.edu} domain is {\tt aries.salleurl.edu}. Two additional name servers are also available, namely {\tt relay1.salleurl.edu} and {\tt relay2.salleurl.edu}.

\subsubsection{Extracted domains and IP addresses}

The {\tt salleurl.edu} domain binds to the IP address {\tt 130.206.42.160}.

Three additional hostnames (the three DNS servers presented in the preceding answer) were also discovered. Their IPs are {\tt 130.206.42.224}, {\tt 130.206.42.224} and {\tt 130.206.42.123} for {\tt aries.}, {\tt relay1.} and {\tt relay2.salleurl.edu}, respectively.

\subsubsection{Purpose of the test}

TODO: ???



\subsection{\texttt{salleurl.edu} authoritative DNS request}

\subsubsection{Primary name server}

The primary name server for the {\tt salleurl.edu} domain is {\tt aries.salleurl.edu}, as clearly indicated by the {\tt MNAME} field of the {\tt SOA} record.

\subsubsection{Extracted domains and IP addresses}

Beside the name servers and the root domain already presented in the previous answer, this test revelaed one more hostname: {\tt columba.salleurl.edu} with the IP address {\tt 130.206.42.238}. Additionally, the four {\tt MX} records state that all of {\tt aries.}, {\tt relay1.}, {\tt relay2.} and {\tt columba.salleurl.edu} are also mail exchange servers.

\subsubsection{Purpose of the test}

The purpose of this test is to retrieve all DNS information (using the {\tt any} flag) for the {\tt salleurl.edu} domain by interrogating the primary name server ({\tt aries.salleurl.edu}) directly and obtaining thus an authoritative answer.



\subsection{\texttt{salleurl.edu} complete DNS listing}

\subsubsection{Purpose of the test}

The prupose of this test is to execute a zone transfer for the {\tt salleurl.edu} domain from one of its name servers. A zone transfer would allow the requester to retrieve all the DNS information for the {\tt salleurl.edu} domain stored on the queried name server.

\subsubsection{Test results}

All three tested name servers ({\tt aries.}, {\tt relay1.} and {\tt relay2.salleurl.edu}) denied the zone transfer and revelead no additional information.
